Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 SupportingInformation.Rmd
Table S1 style modified

knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = c("", ""))%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1),align = "l",line=F)
```

>>>>

knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = NULL)%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1))
```
